---
title: "Homework 1"
author: "Zhiyuan Du"
date: "8/23/2020"
output:
  pdf_document:
    fig_caption: yes
    extra_dependencies: ["float"]
---
This is the homework 1 of ***Zhiyuan Du***. My PID is ***zhiyuan***. 

# Homework 1 
# Zhiyuan Du
# 08/24/2020

```{r setup, include=FALSE}
##### 
##### 
##### Project setup #####
##### 
##### 
##### 
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H", out.extra = "")
library(ggplot2)
##### 
##### 
```

# Problem 2

I have a basic understanding of the R environment after checking out the lectures on the canvas. And I am so excited to set off my R journey and cannot wait to use R Markdown to do my homeworks. There are two parts in the Porblem 2.

## Problem 2 Part A

There are three **desired learning objectives** that I hope to get out of this class:

- Be proficient about using *R Markdown* through the practice.

- Put the *Reproducible Research Concepts* into the real projects.

- Learn to make good *Data cleaning and munging*.

## Problem 2 Part B

1. Normal distribution density function:
\begin{eqnarray}
f(x|\mu,\sigma^2)= \frac{1}{\sigma\sqrt{2\pi}}e^{-\left(\frac{x-\mu^2}{2\sigma^2}\right)};  -\infty<x<\infty,  -\infty<\mu<\infty, \sigma>0
\end{eqnarray} 

2. Binomial distribution density function:
\begin{eqnarray}
P(X=x|n,p)= {{n}\choose{y}}  p^y (1-p)^{n-y},x=0,1,2,...,n;0\le p\le 1 
\end{eqnarray}

3. Poisson distribution density function:
\begin{eqnarray}
P(X=x|\lambda)=\frac{e^{-\lambda}\lambda^x}{x!};x=0,1,...;0\le \lambda<\infty
\end{eqnarray}

# Problem 3

### The 10 rules revealed in the article vividly express what the reproducible computational research is and how to make it perfect. Here are some basic steps I summarized on executing a reproducible compuational research.

* After getting the raw data, make them stored. In this case, each given figure is easily fetched and the plotting procedure could be slightly modified to get results.

* Do the execution and data manipulation steps on the program instead of manually and archive the exact version of the program.

* Record the intermediate results possibly in Standardized Formats.

* Use a vision control system to store all of the scripts.

* Generate Hierarchical Analysis Output, Allowing Layers of Increasing Detail to Be Inspected.

* Give statements to all of the underlying results.

* Make public access to all input data, scripts, versions, parameters, and intermediate results.

# Problem 4

In this problem, I chose the dataframe *'mpg'* in the package of *'ggplot2'*. In the daraframe, there are 11 variables including *'manufacturer'*, *'model'*, *'trans'*, *'drv'*, *'fl'* and *'class'* as the catergorical variable and *'disp'l*, *'year'*, *'cy'l*, '*cty'*, *'hwy'* as the continuous variable.

For the scattter plot, I choose *'year'* as the x-axis and *'displ'* as the y-axis with model added to show the difference within the model.

```{r Problem4a, fig.cap='A scatter plot.', tidy=FALSE, warning=FALSE, fig.height=2.6}
##### 
##### Problem 4: scatter plot #####
##### 
ggplot(data= mpg)+
  geom_point(mapping = aes(x = hwy, y = displ , shape = class)) 

```


From the scatter plot, we can obviously achieve a negative trend between the *'hwy'* and *'displ'*. For the histogram, I choose to use *'model'* as the x-axis and *'hwy'* as the y-axis.

```{r Problem4b, fig.cap='A histogram.', tidy=FALSE, fig.height=4}
##### 
##### Problem 4: histogram #####
##### 
hist(mpg$hwy, main = "Histogram for highway", xlab="highway")

```


---

# Appendix 1: R code


```{r Appendix, ref.label=c("setup","Problem4a","Problem4b"), echo=TRUE, eval=FALSE, tidy=FALSE, include=T}
  
```